Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-21 paper/ijcai/paper.tex
comments

\subsubsection{RQ1: \textit{How often \ds{} misses faulty statements?}}
\label{sec:fault-misses}

In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty statements, 
since it is one of the main issues of dynamic slicing techniques. Table \ref{table:fsws} 
presents the number of faults where at least one of the faulty statements appears 
in the final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. For each fault, we 
only search for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$) of the highest faulty 
classes. \combpar{k} finds the faulty statements faster than 
\sfl{}$^{k}$. Using \combpar{10} we are able to find more $20$ faulty statements than
when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$ of the faulty statements
whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty statements. Thus, \combpar{10} misses less
$5.2\%$ of the faults against \sfl{}$^{10}$.

@@

In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} with \sfl{} to improve \sfl{}.
Table~\ref{table:st}, reports the average rank of all faulty statements of all \dfj{} faults considered
to the study after applying the both techniques, \sfl{}$^{k}$ and \combpar{k} for $K=5$ and $k=10$. $33$ of 
the $260$ faults do not include the faulty statements in the slicer report after slicing. Thus, we report
both values in Table~\ref{table:st}. In bold, we present the results of the $227$ faults that do not
contain the cases where the faulty statements where removed using \combpar{k}. Inside parentheses,
we present the rank results for all faults. The \combpar{k} combination yields an improvement of $13.0$ on the rank mean of the dataset faulty statements when using $K=5$. Instead, if $K=10$ is considered the proposed approach returns an improvement of $11.1$ 
on the rank mean of faulty statements. It is worth noting that Automated Program Repair techniques may directly benefit from this
study to improve their results.
Figure \ref{fig:diagnosis} reports the performance of the diagnosis using \combpar{5} and \combpar{10} against
\sfl{}$^{5}$ and \sfl{}$^{10}$, respectively. Although this dataset has more than 50\% of fault of omissions,
our simple slicing approach was capable of improving the ranking of $97$ for $k=5$ and $117$ for $K=117$ faults. 
Table \ref{table:st} presents the statistics to determine if the observed results are statistically significant. Shapiro-Wilk tests the null hypothesis that results are drawn from a normal distribution. The test is perfomed for all techniques and its variants. With 99\% of confidence, the results tell us that the distributions are not normal. Given that $C$ is not normally distributed, we use the non-parametrical statistical hypothesis test, Friedman. The null-hypothesis is that the ranking results of all techniques and variants are the same. With 99\% of confidence, the results show that the distributions are distinct. In order to understand if there exist a pair of distributions that are equal, we performed a Siegel post-hoc analysis. Figure \ref{fig:performance} reports the results of Siegel analysis for all the distributions. With 99\% of confidence, it is possible to see that in general the distributions are very similar.

>>>>

\subsubsection{RQ1: \textit{How often does \ds{} misses faulty statements?}}
\label{sec:fault-misses}

In \textbf{RQ1}, our concern is to evaluate how often \ds{} misses faulty
statements,  since it is one of the main issues of dynamic slicing techniques.
This is particularly important because when \ds{} missing a faulty statement
means that it will not be in the diagnostic report and therefore has a negative
impact in the fault localization accuracy. Table \ref{table:fsws}  presents the
number of faults where at least one of the faulty statements appears  in the
final reports of both techniques, \sfl{}$^{k}$ and \combpar{k}. For each fault,
we  only search for faulty statements in the top $5$ ($k=5$) and $10$ ($k=10$)
of the highest faulty  classes. \combpar{k} finds the faulty statements faster
than  \sfl{}$^{k}$. \Rui{Starting from here, I don't see the connection with
the rq... the rq has nothing to do with the combination. We need to somehow
motivate why we are discussing these numbers here.}
Using \combpar{10} we are able to find more $20$ faulty
statements than when only using \sfl{}$^{10}$. \combpar{10} only misses $11.8\%$
of the faulty statements whereas \sfl{}$^{10}$ misses $17.9\%$ of the faulty
statements. Thus, \combpar{10} misses less $5.2\%$ of the faults against
\sfl{}$^{10}$.

@@

In \textbf{RQ2}, we intend to evaluate the impact of combining \ds{} with \sfl{}
to improve fault localization. Table~\ref{table:st}, reports the average rank of all faulty
statements of the \dfj{} faults considered to the study after applying the both
techniques, \sfl{}$^{k}$ and \combpar{k} for $K=5$ and $k=10$. We observe that
$33$ of the $260$ \Rui{Ehmm... is this in sycn with previous section?}
faulty versions do not include the faulty statements in the slicer report after slicing.
Thus, we report both values in Table~\ref{table:st}. In bold, we present the
results of the $227$ faults that do not contain the cases where the faulty
statements where removed using \combpar{k}. Inside parentheses, we present the
rank results for all faults. The \combpar{k} combination yields an improvement
of $13.0$ on the rank mean of the dataset faulty statements when using $K=5$.
Instead, if $K=10$ is considered the proposed approach returns an improvement of
$11.1$ on the rank mean of faulty statements.
\Rui{APR doesn't belong here, maybe the last thing to discuss in this section,
but not here in the middle}
It is worth noting that Automated
Program Repair techniques may directly benefit from this study to improve their
results. Figure \ref{fig:diagnosis} reports the performance of the diagnosis
using \combpar{5} and \combpar{10} against \sfl{}$^{5}$ and \sfl{}$^{10}$,
respectively. Although this dataset has more than 50\% of fault of omissions,
our simple slicing approach was capable of improving the ranking of $97$ for
$k=5$ and $117$ for $K=117$ faults. Table \ref{table:st} presents the statistics
to determine if the observed results are statistically significant. Shapiro-Wilk
tests the null hypothesis that results are drawn from a normal distribution. The
test is perfomed for all techniques and its variants. With 99\% of confidence,
the results tell us that the distributions are not normal. Given that $C$ is not
normally distributed, we use the non-parametrical statistical hypothesis test,
Friedman. The null-hypothesis is that the ranking results of all techniques and
variants are the same. With 99\% of confidence, the results show that the
distributions are distinct. To understand if there exist a pair of
distributions that are equal \Rui{equal? isn't this test the effect size?}, we performed a Siegel post-hoc analysis. Figure
\ref{fig:performance} reports the results of Siegel analysis for all the
distributions. With 99\% of confidence, it is possible to see that in general
the distributions are very similar. \Rui{so??}

\Rui{Weakness: there has to be discussion on whether there is potential/promising
results somewhere.}
